---
title: "Manual tests — save_docx()"
output: rmarkdown::github_document
---

This file contains self-contained code snippets for **manual inspection** of
`save_docx()` output. Run each chunk individually, open the resulting `.docx`
file and verify the output looks as expected.

```{r setup, include=FALSE}
library(pager)
library(gtsummary)
library(ggplot2)

# shared sample table used across all gtsummary / gt / flextable snippets
tbl <-
  cards::ADAE[1:150, ] |>
  gtsummary::tbl_hierarchical(
    variables = c(AESOC, AETERM),
    by = TRTA,
    denominator = cards::ADSL,
    id = USUBJID,
  )
```

---

## 1. `gtsummary` table

```{r gtsummary-single}
out <- file.path(tempdir(), "docx_gtsummary.docx")
tbl |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 2. `gt_tbl` table (via `gtsummary::as_gt()`)

```{r gt-single}
out <- file.path(tempdir(), "docx_gt.docx")
tbl |>
  gtsummary::as_gt() |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 3. `gt_tbl` with manual column widths

```{r gt-col-width}
out <- file.path(tempdir(), "docx_gt_colwidth.docx")
tbl |>
  gtsummary::as_gt() |>
  gt::cols_width(dplyr::everything() ~ gt::px(20)) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 4. `flextable` table (autofit layout)

```{r flextable-autofit}
out <- file.path(tempdir(), "docx_flextable_autofit.docx")
tbl |>
  gtsummary::as_flex_table() |>
  flextable::set_table_properties(layout = "autofit") |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 5. `flextable` with manual column widths

```{r flextable-col-width}
out <- file.path(tempdir(), "docx_flextable_colwidth.docx")
tbl |>
  gtsummary::as_flex_table() |>
  flextable::width(j = 1, width = 2) |>
  flextable::width(j = 2:3, width = 1.5) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 6. Paginated table (list of `gtsummary` objects)

```{r gtsummary-paginated}
out <- file.path(tempdir(), "docx_gtsummary_paginated.docx")
gtsummary::tbl_split_by_rows(tbl, row_numbers = seq(20, nrow(tbl), by = 20)) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 7. Paginated table (list of `gt_tbl` objects)

```{r gt-paginated}
out <- file.path(tempdir(), "docx_gt_paginated.docx")
gtsummary::tbl_split_by_rows(tbl, row_numbers = seq(20, nrow(tbl), by = 20)) |>
  purrr::map(gtsummary::as_gt) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 8. Paginated table (list of `flextable` objects)

```{r flextable-paginated}
out <- file.path(tempdir(), "docx_flextable_paginated.docx")
gtsummary::tbl_split_by_rows(tbl, row_numbers = seq(20, nrow(tbl), by = 20)) |>
  purrr::map(gtsummary::as_flex_table) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 9. `ggplot` figure

```{r ggplot}
out <- file.path(tempdir(), "docx_ggplot.docx")
p <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(title = "Motor Trend Cars", x = "Weight (1000 lbs)", y = "Miles per gallon")
save_docx(p, path = out)
message("Output: ", out)
```

---

## 10. `grob` (grid graphic)

```{r grob}
out <- file.path(tempdir(), "docx_grob.docx")
  
x <- (grid::circleGrob() |>
  save_docx(path = out))
message("Output: ", out)
```

---

## 11. Mixed list (`ggplot` + `grob`)

```{r mixed-list}
out <- file.path(tempdir(), "docx_mixed_list.docx")
p <- ggplot(mtcars, aes(x = wt, y = mpg)) + geom_point()
g <- grid::circleGrob()
list(p, g) |>
  save_docx(path = out)
message("Output: ", out)
```

---

## 12. Landscape orientation (custom `reference_docx`)

```{r landscape}
out <- file.path(tempdir(), "docx_landscape.docx")
tbl |>
  gtsummary::as_gt() |>
  save_docx(
    path = out,
    reference_docx = pager::get_reference_docx("landscape")
  )
message("Output: ", out)
```
