---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pager

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/pager)](https://CRAN.R-project.org/package=pager)
[![R-CMD-check](https://github.com/insightsengineering/pager/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/insightsengineering/pager/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/insightsengineering/pager/graph/badge.svg)](https://app.codecov.io/gh/insightsengineering/pager)
<!-- badges: end -->

The pager package makes it simple to save tables of class gtsummary, gt, and flextable as a Word document using a reference document.
This is accomplished by creating the document via R markdown using the `reference_docx:` field.

The package also supports lists of table objects.
When a list is passed, a page break is placed between each table in the list.

## Installation

You can install the development version of pager from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("insightsengineering/pager")
```

## Example

To begin, let's create a summary table.

```{r example}
library(pager)

# create table
tbl <-
  cards::ADAE[1:150, ] |>
  gtsummary::tbl_hierarchical(
    variables = c(AESOC, AETERM),
    by = TRTA,
    denominator = cards::ADSL,
    id = USUBJID,
  )
```

The code below will save the table as  Word document using the default portrait orientation reference document.

```{r table}
gtsummary::as_flex_table(tbl) |>
  save_with_rmarkdown(path = tempfile(fileext = ".docx"))
```

The example below first splits the summary table into a list of tables.
Each table is saved to a separate page in the resulting Word document.

```{r table-list}
gtsummary::tbl_split_by_rows(tbl, row_numbers = seq(20, nrow(tbl), by = 20)) |>
  save_with_rmarkdown(path = tempfile(fileext = ".docx"))
```
