---
title: "Customized Document"
author: "Your Name"
output:
  word_document
---

<!-- Embed CSS for Word output -->
<style>
  /* Set default font size for the entire document */
  body {
    font-size: 12pt;
    font-family: Arial, sans-serif;
  }

  /* Customize headings */
  h1 {
    font-size: 18pt;
    color: #2c3e50;
    font-weight: bold;
    text-align: center;
  }

  h2 {
    font-size: 16pt;
    color: #3498db;
    font-weight: bold;
  }

  h3 {
    font-size: 14pt;
    color: #e74c3c;
    font-style: italic;
  }

  /* Customize paragraphs */
  p {
    font-size: 11pt;
    line-height: 1.5;
    text-align: justify;
  }

  /* Customize lists */
  ul, ol {
    font-size: 11pt;
    margin-left: 20pt;
  }

  /* Customize tables */
  table {
    font-size: 14pt;
    border-collapse: collapse;
    width: 100%;
  }

  th, td {
    border: 1px solid #ddd;
    padding: 8pt;
    text-align: left;
  }

  th {
    background-color: #f2f2f2;
    font-weight: bold;
  }

  /* Customize code blocks */
  pre {
    font-size: 10pt;
    background-color: #f8f8f8;
    border: 1px solid #ddd;
    padding: 10pt;
    overflow-x: auto;
  }

  /* Customize blockquotes */
  blockquote {
    font-size: 11pt;
    font-style: italic;
    border-left: 3px solid #3498db;
    padding-left: 10pt;
    margin-left: 0;
    color: #7f8c8d;
  }
</style>

# This is a Heading 1

This is a paragraph with customized font size and alignment. The font size is set to 11pt, and the text is justified.

## This is a Heading 2

This is another paragraph. The font family is set to Arial.

### This is a Heading 3

This is a paragraph with a different font size and style.

#### Unordered List Example
- Item 1
- Item 2
- Item 3

#### Ordered List Example
1. First item
2. Second item
3. Third item

#### Table Example

| Column 1 | Column 2 | Column 3 |
|----------|----------|----------|
| Row 1    | Data     | Data     |
| Row 2    | Data     | Data     |

#### Code Block Example
```r
# This is an R code block
x <- 1:10
print(x)
```

#### Executed code block
```{r}
# This code will be executed and the output will be shown
summary(cars)
```

#### gtsummary Table Example
```{r}
# Create a simple table using gtsummary
library(gtsummary)

# Create a sample dataset
data <- data.frame(
  age = c(25, 30, 35, 40, 45),
  gender = c("Male", "Female", "Male", "Female", "Male"),
  bmi = c(22.5, 24.1, 26.8, 23.7, 28.2),
  cholesterol = c(180, 195, 210, 190, 220)
)

# Create a gtsummary table
tbl_summary(data, by = "gender")
```